\documentclass{resume}
\usepackage[hidelinks]{hyperref}
\usepackage{lipsum}
\usepackage{setspace}

\name{Walter Tay Ann Lee}
\contact{\href{tel:+65 9868 6218}{+65 9868 6218}}
\contact{\href{mailto:waltertay@u.nus.edu}{waltertay@u.nus.edu}}
\contact{\href{https://www.waltertay.com}{waltertay.com}}

\begin{document}
\makeheader

\begin{ResumeSection}{Relevant Experience}
    \begin{ResumeSubsection}{org=igloocompany,location={Singapore},position={Assistant Product Manager},duration=July 2020 - Current}
    
    igloocompany is a fast growing startup that is revolutionizing the smart access industry in both consumer and enterprise spaces with its proprietary algoPIN\textsuperscript{TM} technology.
    \vspace{0.2cm}
        \begin{itemize}
        \setlength\itemsep{0.05cm}
            \item Product Owner of the igloohome app, iglooworks app, and iglooworks dashboard. I supported the doubling of our YoY revenue by being the only Software Product Manager leading the software release of 11 smart devices and an API product.
            \item Independently resolved issues related to our company's high turnover, in particular: the departure of 2 Head of Products, our Software Product Manager, and our Operations team. This included orchestrating development on both our consumer and enterprise segments, roadmap planning, and doing my best to keep the company operational in general.
            \item Proposed, managed, and designed (designer was sick) an automated test app which would automate operations involved in outgoing quality control. This doubled the velocity of software development for our Korean manufactured products.
            \item Obtained software from the leading researcher in the field of practical combinatorial testing and received consent to use it in a commercial setting. I gave a comprehensive lecture on practical combinatorial testing to our quality assurance team, and this software was subsequently used to generate a combinatorial test plan for the Bridge (a pull-through revenue strategy product).
            \item Introduced the concept of Tidy Data to our Software Engineers. This led to the new firmware versioning information database, which matches best practices around data management and recursively identifies the correct firmware version to upgrade to.
            \item Independently identified design flaws with the linking behaviour of two smart devices by reading technical documentation and proposed new designs that would resolve them.
            \item Spearheaded an app review initiative in order to improve the app rating. This initiative led to an average 1.7 stars increase to a user's rating after receiving a reply to their original review.
            \item Spearheaded the redesign of an IP Protection System to be highly tolerant of human error. This redesign eliminated defects before they could occur, eliminated many operations related to quality control, and provided immediate resolution steps through better error messaging. Additionally, I personally designed and performed all testing around this system.
        \end{itemize}
    \end{ResumeSubsection}

    \begin{ResumeSubsection}{org={Robert Bosch},location={Singapore},position={Corporate Research Intern},duration={July 2018 - Dec 2018}}
    
    Robert Bosch is a German multinational engineering and technology company motivated by the desire to develop products that are “Invented for life”.
    \vspace{0.2cm}
        \begin{itemize}
        \setlength\itemsep{0.05cm}
            \item Developed hardware and software for evaluating commercially available pressure, ultrasonic, TVOC, and TOF sensors.
            \item Conducted wind tunnel experiments to study sensor output from filters at different contamination levels and recommended the most promising sensing principle.
        \end{itemize}
    \end{ResumeSubsection}
\end{ResumeSection}

\begin{ResumeSection}{education}
    \begin{ResumeSubsection}{org={National University of Singapore},position={Bachelor of Mechanical Engineering, Honours (Distinction)},duration={August 2016 - May 2020}}
    \vspace{0.2cm}
    \begin{itemize}
    \setlength\itemsep{0.05cm}
        \item ASEAN Undergraduate Scholarship - a prestigious full-ride scholarship for international students
        \item University Scholars Programme - a unique interdisciplinary curriculum at NUS
    \end{itemize}
    \end{ResumeSubsection}
    \begin{ResumeSubsection}{org={Bilkent University},position={Semester abroad in Ankara, Turkey},duration={Jan 2019 - May 2019}}
    \end{ResumeSubsection}
\end{ResumeSection}

\newpage
\begin{ResumeSection}{projects}
    \begin{itemize}
    \setlength\itemsep{0.05cm}
        \item Deep Reinforcement Learning for Mapless Navigation\hfill{\em{Aug 2019 – May 2020}}
        \item Automated Mobile Gangway for PSA Marine\hfill{\em{Aug 2019 – Dec 2019}}
        \item 2D Finite Element Software Design\hfill{\em{Jan 2019 – May 2019}}
    \end{itemize}
\end{ResumeSection}


\begin{ResumeSection}{skills}
    \begin{itemize}
    \setlength\itemsep{0.05cm}
        \item \textbf{Technical}: Python, C, Lisp, MATLAB, Arduino, TensorFlow, VBA
        \item \textbf{Language}: Native in English, proficient in Malay, conversational in Chinese, Hokkien, and basic Japanese
    \end{itemize}
\end{ResumeSection}

\begin{ResumeSection}{coursework}
    \begin{itemize}
    \setlength\itemsep{0.05cm}
        \item \textbf{Engineering}: Deep Reinforcement Learning, Finite Elements, Mechatronic Systems, Feedback Control Systems, Materials for Engineers, Manufacturing Processes, Project Management
        \item \textbf{Liberal Arts}: Quantum Computation, 'Language, Cognition, and Culture', Mathematics and Reality, Brain and Behaviour, 'Cultures, Civilizations, and Ideas', War and Democracy, Issues In and Around Justice
    \end{itemize}
\end{ResumeSection}


\end{document}


